---
title: "Transatlantic Sentiment"
output: html_document
date: "2025-11-16"
---

```{r setup, include=FALSE}
library(mice)
library(naniar)
library(tidyverse)
library(rio)
library(foreign)
library(tidylog)
library(Hmisc)
library(jtools)
library(performance)  
library(see)    
library(patchwork) 
library(qqplotr)
library(plm)
library(ggplot2)
library(stargazer)
library(broom)
library(dplyr)
library(tidyr)
library(stringr)
library(lmtest)
```

##Load the Data

This loads the data into RStudio, makes a copy of the original data, and restructure the original data into a country-year level data to prepare for panel data regression with country or year fixed effects.

```{r}
setwd ("/Users/hkwang9/Library/CloudStorage/OneDrive-TheUniversityofChicago/University of Chicago/Academics/3 MACSS/Thesis/Data")
data <- import("Transatlantic Emotions Dataset.dta")
data0 <- data

#make a copy of the original data
ex_country <- c("Sweden", "Iceland")
data1 <- data0 %>% 
  filter(! country %in% ex_country)

#restructure the data into panel data structure 
p_data <- pdata.frame(data1, index = c("ccode", "year"))
```

##Begin the analysis

###The full model

```{r}
full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1), data = p_data, subset = NATO == 1, model = "pooling")
summary(full)

full_fe <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1), data = p_data, subset = NATO == 1, model = "within")
summary(full_fe)

full2 <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = NATO == 1, model = "pooling")
summary(full2)

full2_fe <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = NATO == 1, model = "within")
summary(full2_fe)
```


```{r}
library(tidyverse)
library(broom)

# --- Tidy model outputs ---
models_list <- list(
  "Pooling, no controls"      = full,
  "FE, no controls"           = full_fe,
  "Pooling, with controls"    = full2,
  "FE, with controls"         = full2_fe
)

coef_df <- imap_dfr(models_list, ~ {
  tidy(.x) %>%
    mutate(model = .y)
}) %>%
  filter(str_detect(term, "lag\\(")) %>%
  mutate(
    term = term %>%
      str_remove("lag\\(") %>%
      str_remove(", 1\\)") %>%
      str_c(" (t−1)"),
    conf.low  = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error,
    model = factor(model, levels = names(models_list))
  )

# --- Plot ---
model_colors <- c(
  "Pooling, no controls"   = "#378ADD",
  "FE, no controls"        = "#1D9E75",
  "Pooling, with controls" = "#D85A30",
  "FE, with controls"      = "#7F77DD"
)

ggplot(coef_df, aes(x = estimate, y = term, color = model)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60", linewidth = 0.4) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0,
    linewidth = 0.8,
    position = position_dodgev(height = 0.6)
  ) +
  geom_point(
    size = 2.5,
    position = position_dodgev(height = 0.6)
  ) +
  scale_color_manual(values = model_colors) +
  scale_y_discrete(limits = rev) +
  labs(
    x     = "Coefficient estimate (95% CI)",
    y     = NULL,
    color = NULL,
    caption = "Whiskers = 95% CI. Outcome: RDef. Sample: NATO = 1."
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position   = "top",
    legend.text       = element_text(size = 11),
    panel.grid.major.y = element_blank(),
    panel.grid.minor   = element_blank(),
    axis.text.y        = element_text(color = "grey20"),
    plot.caption       = element_text(size = 9, color = "grey50")
  )
```
###The European Model 

```{r}
EU <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1), data = p_data, subset = EU == 1, model = "pooling")
summary(EU)

EU_fe <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1), data = p_data, subset = EU == 1, model = "within")
summary(EU_fe)

EU2 <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = EU == 1, model = "pooling")
summary(EU2)

EU2_fe <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = EU == 1, model = "within")
summary(EU2_fe)
```
### The Demorcrat Model 

```{r}
dem <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1), data = p_data, subset = party == "Democrat", model = "pooling")
summary(dem)

dem_fe <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1), data = p_data, subset = party == "Democrat", model = "within")
summary(dem_fe)

dem2 <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = party == "Democrat", model = "pooling")
summary(dem2)


dem2_fe <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = party == "Democrat", model = "within")
summary(dem2_fe)

```

### The Republican Model 

```{r}
gop <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1), data = p_data, subset = party == "Republican", model = "pooling")
summary(gop)

gop_fe <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1), data = p_data, subset = party == "Republican", model = "within")
summary(gop_fe)

gop2 <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = party == "Republican", model = "pooling")
summary(gop2)


gop2_fe <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = party == "Republican", model = "within")
summary(gop2_fe)

```

##Alternative Explanations 

### fri 

```{r}
fri <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) +  lag(surprise, 1) + lag(fri, 1), data = p_data, subset = EU == 1, model = "pooling")
summary(fri)

fri_fe <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(fri, 1), data = p_data, subset = EU == 1, model = "within")
summary(fri_fe)

fri2 <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(fri, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = EU == 1, model = "pooling")
summary(fri2)

fri2_fe <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(fri, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = EU == 1, model = "within")
summary(fri2_fe)
```




### proximity 

```{r}
proxy_raw <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + log_proxy + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = NATO == 1, model = "pooling")
summary(proxy_raw)

proxy_EU <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + log_proxy + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = EU == 1, model = "pooling")
summary(proxy_EU)

proxy_Dem <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + log_proxy + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = party == "Democrat", model = "pooling")
summary(proxy_Dem)

proxy_GOP <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + log_proxy + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = party == "Republican", model = "pooling")
summary(proxy_GOP)

```

##sewing the regression results together 

```{r}
# =========================================================
# 0) Shared labels / settings
# =========================================================
col_labels <- c("Full Model", "European Model", "Democrat Model", "Republican Model")

stars_cutoffs <- c(0.1, 0.05, 0.01)

note_html <- "* p < 0.1; ** p < 0.05; *** p < 0.01"
note_tex  <- "$^{*}$ p < 0.1; \\, $^{**}$ p < 0.05; \\, $^{***}$ p < 0.01"

# Labels for NO-control models (Tables 2 & 3): emotions only
cov_labels_nocontrol <- c(
  "Anger (1-year lag)",
  "Fear (1-year lag)",
  "Joy (1-year lag)",
  "Sadness (1-year lag)",
  "Disgust (1-year lag)",
  "Surprise (1-year lag)"
)

# Labels for control models (Tables 4 & 5): emotions + controls
cov_labels_control <- c(
  "Anger (1-year lag)",
  "Fear (1-year lag)",
  "Joy (1-year lag)",
  "Sadness (1-year lag)",
  "Disgust (1-year lag)",
  "Surprise (1-year lag)",
  "Sentiment (1-year lag)",
  "Liberal Democracy Index (1-year lag)",   # Dem
  "Intrastate Conflict (1-year lag)"
)

# =========================================================
# 1) Helper: drop controls from a model (for Tables 2 & 3)
#    Controls = lag(Sentiment,1) + lag(Dem,1) + lag(IntrastCon,1)
# =========================================================
drop_controls <- function(model_obj) {
  # Uses update() so you do not need to rewrite the full formula.
  # If a term isn't present, update() will just ignore it safely.
  update(
    model_obj,
    . ~ . -
      lag(Sentiment, 1) -
      lag(Dem, 1) -
      lag(IntrastCon, 1)
  )
}

# =========================================================
# 2) TEX post-processing: enforce letter-width fit + 1.0 spacing
#    Requires in LaTeX preamble:
#      \usepackage{setspace}
#      \usepackage{adjustbox}
# =========================================================
wrap_tex_letter_single <- function(tex_file) {
  x <- readLines(tex_file, warn = FALSE)

  # Insert after \centering
  x <- gsub(
    "\\\\centering",
    "\\\\centering\n\\\\setstretch{1.0}\n\\\\adjustbox{max width=\\\\textwidth}{",
    x
  )

  # Close adjustbox before \end{table}
  x <- gsub(
    "\\\\end\\{table\\}",
    "}\n\\\\end{table}",
    x
  )

  writeLines(x, tex_file)
}

# =========================================================
# 3) Writers: DOC (HTML) + TEX (LaTeX)
# =========================================================
make_doc <- function(models, outfile, cov_labels, controls_yesno, fe_yesno) {
  stargazer(
    models[[1]], models[[2]], models[[3]], models[[4]],
    type = "html",
    column.labels = col_labels,
    column.separate = c(1, 1, 1, 1),
    covariate.labels = cov_labels,
    star.cutoffs = stars_cutoffs,
    notes = note_html,
    notes.append = FALSE,
    notes.align = "l",
    add.lines = list(
      c("Controls", controls_yesno, controls_yesno, controls_yesno, controls_yesno),
      c("Country Fixed Effects", fe_yesno, fe_yesno, fe_yesno, fe_yesno)
    ),
    out = outfile
  )
}

make_tex <- function(models, outfile, cov_labels, controls_yesno, fe_yesno) {
  stargazer(
    models[[1]], models[[2]], models[[3]], models[[4]],
    type = "latex",
    column.labels = col_labels,
    column.separate = c(1, 1, 1, 1),
    covariate.labels = cov_labels,
    star.cutoffs = stars_cutoffs,
    notes = note_tex,
    notes.append = FALSE,
    notes.align = "l",
    add.lines = list(
      c("Controls", controls_yesno, controls_yesno, controls_yesno, controls_yesno),
      c("Country Fixed Effects", fe_yesno, fe_yesno, fe_yesno, fe_yesno)
    ),
    out = outfile
  )

  wrap_tex_letter_single(outfile)
}

# =========================================================
# 4) Build model sets
#    IMPORTANT CHANGE:
#      Table 2 & 3 "Full Model" will be re-estimated WITHOUT controls.
# =========================================================

# --- Tables 2 & 3: NO controls in ANY column ---
full_nc    <- drop_controls(full)
full_fe_nc <- drop_controls(full_fe)

m_table2 <- list(full_nc,    EU,    dem,    gop)      # no control, no FE
m_table3 <- list(full_fe_nc, EU_fe, dem_fe, gop_fe)  # no control, FE

# --- Tables 4 & 5: WITH controls (keep as your existing objects) ---
m_table4 <- list(full2,    EU2,    dem2,    gop2)       # control, no FE
m_table5 <- list(full2_fe, EU2_fe, dem2_fe, gop2_fe)    # control, FE

# =========================================================
# 5) Generate DOC + TEX outputs
# =========================================================

# Table 2: no control, no FE
make_doc(m_table2, "table2.doc", cov_labels_nocontrol, controls_yesno = "No",  fe_yesno = "No")
make_tex(m_table2, "table2.tex", cov_labels_nocontrol, controls_yesno = "No",  fe_yesno = "No")

# Table 3: no control, FE
make_doc(m_table3, "table3.doc", cov_labels_nocontrol, controls_yesno = "No",  fe_yesno = "Yes")
make_tex(m_table3, "table3.tex", cov_labels_nocontrol, controls_yesno = "No",  fe_yesno = "Yes")

# Table 4: controls, no FE
make_doc(m_table4, "table4.doc", cov_labels_control,   controls_yesno = "Yes", fe_yesno = "No")
make_tex(m_table4, "table4.tex", cov_labels_control,   controls_yesno = "Yes", fe_yesno = "No")

# Table 5: controls, FE
make_doc(m_table5, "table5.doc", cov_labels_control,   controls_yesno = "Yes", fe_yesno = "Yes")
make_tex(m_table5, "table5.tex", cov_labels_control,   controls_yesno = "Yes", fe_yesno = "Yes")

message("Done. Updated table2–table5 as .doc and .tex (T2/T3 have NO controls).")

```


##Alternative Explanations 

### fri 

```{r}
fri <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) +  lag(surprise, 1) + lag(fri, 1), data = p_data, subset = EU == 1, model = "pooling")
summary(fri)

fri_fe <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(fri, 1), data = p_data, subset = EU == 1, model = "within")
summary(fri)

fri2 <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(fri, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = EU == 1, model = "pooling")
summary(fri2)

fri2_fe <- full <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + lag(fri, 1) + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = EU == 1, model = "within")
summary(fri2_fe)
```

### proximity 

```{r}
proxy_raw <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + log_proxy + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = NATO == 1, model = "pooling")
summary(proxy_raw)

proxy_EU <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + log_proxy + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = EU == 1, model = "pooling")
summary(proxy_EU)

proxy_Dem <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + log_proxy + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = party == "Democrat", model = "pooling")
summary(proxy_Dem)

proxy_GOP <- plm(RDef ~ lag(anger, 1) + lag(fear, 1) + lag(joy, 1) + lag(sadness, 1) + lag(disgust, 1) + lag(surprise, 1) + log_proxy + lag(Sentiment, 1) + lag(Dem, 1) + lag(IntrastCon, 1), data = p_data, subset = party == "Republican", model = "pooling")
summary(proxy_GOP)

```


```{r}
# =========================================================
# Sew fri models into one table (4 columns)
#   (1) Pooling: emotions + fri
#   (2) FE:      emotions + fri
#   (3) Pooling: emotions + fri + controls
#   (4) FE:      emotions + fri + controls
# =========================================================

# Column labels for this table
col_labels_fri <- c("Pooling", "FE (within)", "Pooling + Ctrls", "FE + Ctrls")

# Covariate labels (match model order)
cov_labels_fri_all <- c(
  "Anger (1-year lag)",
  "Fear (1-year lag)",
  "Joy (1-year lag)",
  "Sadness (1-year lag)",
  "Disgust (1-year lag)",
  "Surprise (1-year lag)",
  "Fiscal Rule Index (1-year lag)",  # lag(fri, 1)
  "Sentiment (1-year lag)",
  "Liberal Democracy Index (1-year lag)",      # Dem
  "Intrastate Conflict (1-year lag)"
)

# Model list (4 columns)
m_fri <- list(fri, fri_fe, fri2, fri2_fe)

# ---------- HTML (for your Rmd / html_document) ----------
stargazer(
  m_fri[[1]], m_fri[[2]], m_fri[[3]], m_fri[[4]],
  type = "html",
  column.labels = col_labels_fri,
  column.separate = c(1, 1, 1, 1),
  covariate.labels = cov_labels_fri_all,
  star.cutoffs = stars_cutoffs,
  notes = note_html,
  notes.append = FALSE,
  notes.align = "l",
  add.lines = list(
    c("Sample", "EU only", "EU only", "EU only", "EU only"),
    c("Controls", "No", "No", "Yes", "Yes"),
    c("Country Fixed Effects", "No", "Yes", "No", "Yes")
  ),
  out = "table_fri.doc"
)

# ---------- LaTeX ----------
stargazer(
  m_fri[[1]], m_fri[[2]], m_fri[[3]], m_fri[[4]],
  type = "latex",
  column.labels = col_labels_fri,
  column.separate = c(1, 1, 1, 1),
  covariate.labels = cov_labels_fri_all,
  star.cutoffs = stars_cutoffs,
  notes = note_tex,
  notes.append = FALSE,
  notes.align = "l",
  add.lines = list(
    c("Sample", "EU only", "EU only", "EU only", "EU only"),
    c("Controls", "No", "No", "Yes", "Yes"),
    c("Country Fixed Effects", "No", "Yes", "No", "Yes")
  ),
  out = "table6.tex"
)

wrap_tex_letter_single("table6.tex")

message("Done. Wrote table6.doc and table6.tex")

# =========================================================
# Sew proximity models into one table (4 columns, pooling)
#   (1) Full/NATO
#   (2) European (EU)
#   (3) Democrat
#   (4) Republican
# =========================================================

# Column labels (match your main tables)
col_labels_proxy <- c("Full Model", "European Model", "Democrat Model", "Republican Model")

# Covariate labels (match model formula order)
cov_labels_proxy_all <- c(
  "Anger (1-year lag)",
  "Fear (1-year lag)",
  "Joy (1-year lag)",
  "Sadness (1-year lag)",
  "Disgust (1-year lag)",
  "Surprise (1-year lag)",
  "Geographic Proximity (log)",              # log_proxy
  "Sentiment (1-year lag)",
  "Liberal Democracy Index (1-year lag)",    # Dem
  "Intrastate Conflict (1-year lag)"
)

# Model list (4 columns)
m_proxy <- list(proxy_raw, proxy_EU, proxy_Dem, proxy_GOP)

# ---------- HTML (for your Rmd / html_document) ----------
stargazer(
  m_proxy[[1]], m_proxy[[2]], m_proxy[[3]], m_proxy[[4]],
  type = "html",
  column.labels = col_labels_proxy,
  column.separate = c(1, 1, 1, 1),
  covariate.labels = cov_labels_proxy_all,
  star.cutoffs = stars_cutoffs,
  notes = note_html,
  notes.append = FALSE,
  notes.align = "l",
  add.lines = list(
    c("Controls", "Yes", "Yes", "Yes", "Yes"),
    c("Country Fixed Effects", "No", "No", "No", "No")
  ),
  out = "table7.doc"
)

# ---------- LaTeX ----------
stargazer(
  m_proxy[[1]], m_proxy[[2]], m_proxy[[3]], m_proxy[[4]],
  type = "latex",
  column.labels = col_labels_proxy,
  column.separate = c(1, 1, 1, 1),
  covariate.labels = cov_labels_proxy_all,
  star.cutoffs = stars_cutoffs,
  notes = note_tex,
  notes.append = FALSE,
  notes.align = "l",
  add.lines = list(
    c("Controls", "Yes", "Yes", "Yes", "Yes"),
    c("Country Fixed Effects", "No", "No", "No", "No")
  ),
  out = "table7.tex"
)

wrap_tex_letter_single("table7.tex")

message("Done. Wrote table7.doc and table7.tex")
```



